Autogenerated Questions Paper Draft

### 2018-05-06 paper_draft/paper_draft.tex
Add distractor examples for all categories up to functions

\usepackage{courier}
\usepackage{listings}
\lstset{basicstyle=\ttfamily, language=C++, captionpos=b, breaklines=true, float}

@@

\begin{lstlisting}[caption={Expressions Question}, label=lst-expressions_1]
What is the variable "bar" equal to? 
int foo = 2; 
int bar = foo * 4 % 3 + 7; 
\end{lstlisting}

@@

\begin{lstlisting}[caption={Loop Counting Difficulty 1 Example}, label=lst-loop_counting_d1]
How many times does the '*' print? 
for (int b = 4; b < 7; b = b + 1)
{
	cout << '*';
} 
\end{lstlisting}

@@

\begin{lstlisting}[caption={Loop Counting Difficulty 2 Example}, label=lst-loop_counting_d2]
How many times does the '*' print? 
int j = 53;
do 
{
	cout << '*'; 
	j = j - 5; 
} while (j >= 30); 
\end{lstlisting}

@@

\begin{lstlisting}[caption={Loop Counting Difficulty 3 Example}, label=lst-loop_counting_d3]
How many times does the '*' print?
int i = 13; 
while (i >= 3) 
{
	cout << '*'; 
	i /= 2;
}
\end{lstlisting}

@@

\begin{lstlisting}[float, caption={Loop Counting Difficulty 4 Example}, label=lst-loop_counting_4]
How many times does the '*' print? 
for (int i = 43; i >= 20; i = i - 10) 
{ 
	for (int j = 56; j > 45; j = j - 5) 
	{ 
		cout << '*'; 
	} 
}
\end{lstlisting}

@@

\begin{lstlisting}[caption={Loop Printing Difficulty 2 Example}, label=lst-loop_printing]
What is the following output of the code? 
int b = 61; 
do
{ 
	cout << b << ' '; 
	b = b - 10; 
} while (b > 20); 
\end{lstlisting}

Each difficulty is generated using the exact same methods as \textbf{Loop Counting} but obviously has different distractor methods, yet the same distractors are used for each difficulty. The first 
distractor uses all of the same values as the correct answer, except it omits the first value. The second distractor uses the same values as the correct answer, but it appends one more iteration
from the loop. The third distractor is the same values as the correct one, except it omits the last value. Finally, the fourth distractor combines the first two methods by omitting the first value
and appends an extra iteration to the end. While there are many options for generating distractors, these all seem to provide convincing answers that some students may create on their own.

@@

\begin{lstlisting}[caption={\textbf{Switch Cases} Example}, label=lst-switch_cases]
What is the value of "bar" after the switch case block?
int bar = 4; 
switch (bar) { 
	case 2: 
		bar = 5; 
		break; 
	case 4: 
		bar = 6; 
	case 1: 
		bar = 2;
		break; 
	case 3: 
		bar = 0; 
	case 0: 
		bar = 1; 
		break; 
} 
\end{lstlisting}

@@

All distractor methods are also shared between each difficulty, which may be room for improvement, but for now, these methods offer plausible answers for each difficulty. The first distractor is
the original value of the variable. The second distractor is always the value that is \textit{compared} to in the first case (e.g. the value 2 in the example above) and is a good distractor to identify students that are not very familiar with the block. The next two distractors (to be used more generally) are based on some conditions.

@@

\begin{lstlisting}[caption={\textbf{Arrays} Difficulty 1 Example}, label=lst-arrays_1]
What are the contents of the array after the following statements? 
int bar[6] = {6, 5, 3, 8, 1, 9}; 
int temp; 
temp = bar[4]; 
bar[4] = bar[1]; 
bar[1] = temp; 
\end{lstlisting}

@@

\begin{lstlisting}[caption={\textbf{Arrays} Difficulty 2 Example}, label=lst-arrays_2, float]
What are the contents of the array after the following?
int documents[6] = {3, 3, 10, 1, 1, 2};
for (int i = 0; i < 6; i += 1)
{ 
	documents[i] += 5; 
} 
\end{lstlisting}

@@

\begin{lstlisting}[caption={\textbf{Arrays} Difficulty 3 Example}, label=lst-arrays_3]
What is printed after the following statements?
int dogs[6] = {0, 1, 7, 3, 0, 2}; 
for (int i = 1; i < 4; i = i + 1) 
{ 
	cout << dogs[i] << " ";
} 
\end{lstlisting}

>>>>

\usepackage{courier}
\usepackage{listings}
\lstset{basicstyle=\ttfamily, 
	language=C++,
 	literate={~} {$\sim$}{1}, 
	captionpos=b, 
	breaklines=true, 
	float}

@@

\begin{lstlisting}[caption={Expressions Question in GIFT}, label=lst-expressions_1]
What is the variable "bar" equal to? 
int foo = 2; 
int bar = foo * 4 + 8 / 3;
{
	=10
	~5
	~10.667
	~12
	~5.333
}
\end{lstlisting}

@@

\begin{lstlisting}[caption={Loop Counting Difficulty 1 GIFT Example}, label=lst-loop_counting_d1, float]
How many times does the '*' print? 
for (int b = 4; b < 7; b = b + 1)
\{
	cout << '*';
\}
{
	=3
	~2
	~4
	~6
	~7
}
\end{lstlisting}

@@

\begin{lstlisting}[caption={Loop Counting Difficulty 2 GIFT Example}, label=lst-loop_counting_d2, float]
How many times does the '*' print? 
int j = 53;
do 
\{
	cout << '*'; 
	j = j - 5; 
\} while (j >= 30); 
{
	=5
	~4
	~6
	~2
	~1
}
\end{lstlisting}

@@

\begin{lstlisting}[caption={Loop Counting Difficulty 3 GIFT Example}, label=lst-loop_counting_d3]
How many times does the '*' print?
int i = 13; 
while (i >= 3) 
\{
	cout << '*'; 
	i /= 2;
\}
{
	=3
	~2
	~4
	~1
	~6
}
\end{lstlisting}

@@

\begin{lstlisting}[float, caption={Loop Counting Difficulty 4 GIFT Example}, label=lst-loop_counting_4]
How many times does the '*' print? 
for (int i = 43; i >= 20; i = i - 10) 
\{ 
	for (int j = 56; j > 45; j = j - 5) 
	\{ 
		cout << '*'; 
	\} 
\}
{
	=9
	~3
	~4
	~12
	~16
}
\end{lstlisting}

@@

\begin{lstlisting}[caption={Loop Printing Difficulty 2 GIFT Example}, label=lst-loop_printing]
What is the following output of the code? 
int b = 61; 
do
\{ 
	cout << b << ' '; 
	b = b - 10; 
\} while (b > 20);
{
	=61 51 41 31 21
	~51 41 31 21
	~61 51 41 31 21 11
	~61 51 41 31
	~51 41 31 21 11
}
\end{lstlisting}

Each difficulty is generated using the exact same methods as \textbf{Loop Counting} but obviously has different distractor methods, yet the same distractors are used for each difficulty within the \textbf{Loop Printing} category. The first 
distractor uses all of the same values as the correct answer, except it omits the first value. The second distractor uses the same values as the correct answer, but it appends one more iteration
from the loop. The third distractor is the same values as the correct one, except it omits the last value. Finally, the fourth distractor combines the first two methods by omitting the first value
and appends an extra iteration to the end. While there are many options for generating distractors, these all seem to provide convincing answers that some students may create on their own.

@@

\begin{lstlisting}[caption={\textbf{Switch Cases} GIFT Example}, label=lst-switch_cases]
What is the value of "bar" after the switch case block?
int bar = 4; 
switch (bar) \{ 
	case 7: 
		bar = 5; 
		break; 
	case 4: 
		bar = 6; 
	case 1: 
		bar = 2;
		break; 
	case 3: 
		bar = 0; 
\}
{
	=2
	~4
	~7
	~6
	~1
} 
\end{lstlisting}

@@

All distractor methods are also shared between each difficulty, which may be room for improvement, but for now, these methods offer plausible answers for each difficulty. The first distractor is
the original value of the variable. The second distractor is always the value that is \textit{compared} to in the first case (e.g. the value 7 in the example above) and is a good distractor to identify students that are not very familiar with the structure. The next two distractors (to be used more generally) are based on some conditions.

@@

\begin{lstlisting}[caption={\textbf{Arrays} Difficulty 1 GIFT Example}, label=lst-arrays_1]
What are the contents of the array after the following statements? 
int bar[6] = \{6, 5, 3, 8, 1, 9\}; 
int temp; 
temp = bar[4]; 
bar[4] = bar[1]; 
bar[1] = temp;
{
	=\{6, 1, 3, 8, 5, 9\}
	~\{6, 5, 3, 8, 1, 9\}
	~\{8, 5, 3, 6, 1, 9\}
	~\{6, 5, 9, 8, 1, 3\}
	~\{9, 5, 3, 8, 1, 6\}
} 
\end{lstlisting}

@@

\begin{lstlisting}[caption={\textbf{Arrays} Difficulty 2 GIFT Example}, label=lst-arrays_2, float]
What are the contents of the array after the following?
int documents[6] = \{3, 3, 10, 1, 1, 2\};
for (int i = 0; i < 6; i += 1)
\{ 
	documents[i] += 5; 
\}
{
	=\{8, 8, 15, 6, 6, 7\}
	~\{3, 3, 10, 1, 1, 2\}
	~\{9, 9, 16, 7, 7, 8\}
	~\{0, 1, 2, 3, 4, 5\}
	~\{-2, -2, 5, -4, -4, -3\}
} 
\end{lstlisting}

@@

\begin{lstlisting}[caption={\textbf{Arrays} Difficulty 3 GIFT Example}, label=lst-arrays_3, float]
What is printed after the following statements?
int bar[6] = \{4, 10, 4, 6, 9, 2\};
for (int i = 1; i < 6; i = i + 2)
\{
	cout << bar[i] << " ";
\}
{
	=10 6 2 
	~6 2 10 
	~6 10 6 
	~4 4 9 
	~Run-time error due to out of bound index.
}
\end{lstlisting}
